Dashboard section

### 2022-07-29 Report/Draft Dashboard section.Rmd
Syntax highlighting alternatives.

---
title: "Dashboard section"
author: "Torbjørn Skinnemoen Ottersen"
date: '2022-07-23'
output:
  pdf_document: default
  html_document: default
---

@@

>>>>

---
title: "Dashboard section"
author: "Torbjørn Skinnemoen Ottersen"
date: '2022-07-23'
output:
  pdf_document:
    highlight: pygments
  html_document: default
---

@@

<!--# kate, haddock, and pygments are nice code syntax highlighting alternatives to the default -->
